---
title: "Hello R"
author: "Gwendolyn Espinoza"
date: "Data 2401"
output: 
  html_document: 
    fig_width: 8
    fig_height: 7
    highlight: pygments
    theme: yeti
---

MAKE SURE YOU READ AND FOLLOW **ALL** INSTRUCTIONS ON THE INSTRUCTION DOCUMENT. 

### Load packages

```{r load-packages, message=FALSE}
library(tidyverse) 
library(datasauRus)
```


### Exercise 1

```{r frequency table}
datasaurus_dozen %>%
  count(dataset) %>%
  print(13)
```
There are 1846 rows. There are 3 variables named dataset, x, and y.

### Exercise 2

First let's plot the data in the dino dataset:

#### Dino Dataset

```{r plot-dino, fig.height=3, fig.width=6}
 dino_data <- datasaurus_dozen %>%
  filter(dataset == "dino")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```

#### Correlation Coefficient of x and y

```{r cor-dino}
dino_data %>%
  summarize(r = cor(x, y))
```

### Exercise 3

#### Star Dataset

```{r plot-star}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "star")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()
```


#### Correlation Coefficient of x and y

```{r cor-star}
dino_data %>%
  summarize(r = cor(x, y))

```

This number seems to be lower than the dino's. It is also not linear just like the dino's.

### Exercise 4

#### Circle Dataset

```{r circle}
dino_data <- datasaurus_dozen %>%
  filter(dataset == "circle")
ggplot(data = dino_data, mapping = aes(x = x, y = y)) +
  geom_point()

```

#### Correlation Coefficient of x and y

```{r x v y circle}
dino_data %>%
  summarize(r = cor(x, y))

```

This number seems to be lower than the dino's data. It is also not linear. 

### Exercise 5

(Add code and narrative as needed. To add R chunks either type out the backticks, curly braces, and the letter `r` or use the Insert chunk button above, with the green +C.)

#### Dataset For All!
```{r for all}
ggplot(datasaurus_dozen, aes(x = x, y = y, color = dataset))+
  geom_point()+
  facet_wrap(~ dataset, ncol = 3) + # facet the dataset variable, in 3 cols
  theme(legend.position = "none")
```

#### Correlation Coefficient of x and y

```{r comparison x v y}
datasaurus_dozen %>%
  group_by(dataset) %>%
  summarize(r = cor(x, y))
```
